Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect

### 2021-06-01 paper_draft2.tex
gaussian kernel work

\begin{enumerate}
\item if $e^{-y}>m$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
\item if $e^{-y}<m$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
\item if $e^{-y}=m$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
\end{enumerate}
In each case, the number of zero-crossings does not exceed one.
\end{proof}

@@

\begin{equation}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
\begin{equation}\label{laplacew2}
w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winva}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
\end{equation}
with
$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$

The integrals in \eqref{laplacew2} can be computed using elementary methods to obtain
\begin{equation}
w_2(x) = \begin{cases}
-\frac{1}{2}e^{x-w_1^{-1}(a)} + \frac{1}{2}e^{x-w_1^{-1}(b)} & x < w_1^{-1}(b) \\
1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
\frac{1}{2} e^{-(x-w_1^{-1}(a))} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & x > w_1^{-1}(a)
\end{cases}
\end{equation}

>>>>

\begin{enumerate}
\item if $y<\ln\frac{1}{m}$, then $f$ is decreasing on $(0,\infty)$, hence has no zero-crossings;
\item if $y>\ln\frac{1}{m}$, then $f$ has a unique zero-crossing at $x=\frac{1}{2}(y-\ln(m))$;
\item if $y=\ln\frac{1}{m}$, then $f$ vanishes on $(y,\infty)$, hence it has no zero-crossings.
\end{enumerate}
In each case, the number of zero-crossings does not exceed one.
\end{proof}

@@

\begin{equation}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
\begin{equation}\label{laplacew2}
w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winvb}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
\end{equation}
with
$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$

The integrals in \eqref{laplacew2} can be computed using elementary methods to obtain
\begin{equation}
w_2(x) = \begin{cases}
\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
\end{cases}
\end{equation}

We can split into three cases:

\begin{enumerate}
\item $a<\frac{1}{2}$, $b<\frac{1}{2}$. Then
\begin{equation}
w_2(x) = \begin{cases}
\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
\end{cases}
\end{enumerate}
